Attack-Tolerance in Structured Networks via Multipath Routing \\ Draft: 2016-02-18

### 2016-02-21 ec-2016/source/paper.tex
Add beginning of routing overview.

This section gives an informal overview of the multipath routing algorithm.

\begin{table}%
\tbl{Butterfly Multipath Routing Variables\label{tab:routing}}
{
\begin{tabular}{|l|l|}
\hline
NAME & VARIABLE \\\hline
butterfly dimension & $m \in \mathbb{Z}_+$ \\\hline
trust radius & $h \in \mathbb{Z} : 1 \leq h \leq \lfloor m/2 \rfloor$ \\\hline
path index & $s \in \{0,1\}^h$ \\\hline
\end{tabular}
}
\end{table}%

>>>>

This section gives an informal overview of the multipath routing algorithm.
In a wraparound butterfly network with trusted radius $h$,
the algorithm constructs $2^h$ disjoint paths between the trusted neighborhoods
of any two nodes, each parameterized by an $h$-bit string $s$
(see Table \ref{tab:routing}).
Each path cycles around the levels of the butterfly network (about) twice.
During the first cycle, the place-within-level $z$ of all nodes is set such that
no two paths overlap outside the trusted neighborhoods.
During the second cycle, the place-within-level is set to its destination value
and the algorithm terminates when the destination level is reached.

\begin{table}%
\tbl{Butterfly Multipath Routing Variables\label{tab:routing}}
{
\begin{tabular}{|l|l|}
\hline
NAME & VARIABLE \\\hline
butterfly dimension & $m \in \mathbb{Z}_+$ \\\hline
node level & $l \in \mathbb{Z} : 0 \leq l < m$ \\\hline
node place within level & $z \in \mathbb \{0,1\}^m$ \\\hline
trust radius & $h \in \mathbb{Z} : 1 \leq h \leq \lfloor m/2 \rfloor$ \\\hline
path index & $s \in \{0,1\}^h$ \\\hline
\end{tabular}
}
\end{table}%
